% !TEX program = xelatex
\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.65in]{geometry}
\usepackage{graphicx}
\usepackage[pdfnewwindow=true]{hyperref}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage{sectsty}
\usepackage{fontspec}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\pagestyle{fancy}

\definecolor{header-blue}{HTML}{1375CF}
\renewcommand{\headrulewidth}{0pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{-2pt}
\sectionfont{\fontsize{11}{0}\selectfont\MakeUppercase}
\titlespacing*{\section}{0pt}{16pt}{6pt}
\pagenumbering{gobble} % No page number

\setlist[itemize]{noitemsep}
\setlength{\leftmargini}{13pt}

\setmainfont{Open Sans}

\begin{document}

\begin{center}
    {\huge\textbf{Jonathan Sumner Evans}} \\
    \vspace{3pt}
    \faPhone\ +1 (720) 459-1501
    \textbar\ \today
    \textbar\ \href{mailto:sumner.evans98@gmail.com}{\faEnvelope\ sumner.evans98@gmail.com} \\
    \href{https://www.linkedin.com/in/sumnerevans}{\faLinkedin\ linkedin.com/in/sumnerevans}
    \textbar\ \href{https://sumnerevans.com}{\faGlobe\ sumnerevans.com}
    \textbar\ \href{https://gitlab.com/sumner}{\faGitlab\ gitlab.com/sumner}
    \rule{\textwidth}{0.5pt}
\end{center}

\section*{Education}
\textbf{Colorado School of Mines} - Golden, CO - M.S. Computer Science
\hfill Aug. 2018 - May 2019
\begin{itemize}
    \item Working on a project with Dr. Mehta to automate group selection in
        CSCI 406 and improve the algorithms used in that process.
    \item Chair of Mines ACM, Service Chair of Tau Beta Pi, Linux Help Guru of
        Mines Linux Users Group (LUG)
\end{itemize}

\textbf{Colorado School of Mines} - Golden, CO - B.S. Computer Science - 3.9 GPA
\hfill July 2016 - May 2018
\begin{itemize}
    \item Vice President of Mines ACM, Secretary of Mines Linux Users Group
        (LUG)
    \item \textit{Notable Classes:} Operating Systems, Algorithms, Computer
        Graphics, Computer Simulation, Virtual Reality, Principles of
        Programming Languages, Artificial Intelligence, Software Engineering,
        Data Structures
\end{itemize}

\vspace{2pt}
\textbf{Red Rocks Community College} - Lakewood, CO - 67 Credit Hours - 4.0 GPA
\hfill Aug. 2012 - May 2016

\section*{Work Experience}
\textbf{Instructor (Algorithms)} - Colorado School of Mines - Golden, CO
\hfill Aug. 2018 - Present
\begin{itemize}
    \item Teaching a section of CSCI 406 Algorithms this fall.
    \item \textit{Topics include:} analysis of algorithms, evaluation of data
        structures, sorting algorithms, dynamic programming, graph algorithms,
        and NP-completeness.
\end{itemize}

\textbf{Software Engineering Intern} - Pivotal - Denver, CO
\hfill May 2018 - Aug. 2018
\begin{itemize}
    \item Improved system for imaging workstations for consistent workflows on
        all machines used by the Tracker team.
    \item Contributed in a LEAN Product process to identify the needs of the
        Tracker team.
\end{itemize}

\vspace{2pt}
\textbf{CS@Mines on Tour Presenter} - Colorado School of Mines -
Golden, CO \hfill Jan. 2018 - May 2018
\begin{itemize}
    \item Gave presentations and led workshops about CS for middle and high
        school students.
\end{itemize}

\vspace{2pt}
\textbf{Teachers Assistant (Data Structures)} - Colorado School of Mines -
Golden, CO \hfill Aug. 2017 - May 2018

\vspace{2pt}
\textbf{Software Development Intern} - Kenzan - Denver, CO
\hfill June 2017 - Aug. 2017
\begin{itemize}
    \item Contributed to OSS projects on behalf of Kenzan including React and
        Node.
    \item Worked to improve Kenzan website by implementing CI/CD pipeline with
        a WebPack build.
\end{itemize}

\vspace{2pt}
\textbf{Software Developer} - Can/Am Technologies, Inc. - Lakewood, CO
\hfill July 2013 - Aug. 2016
\begin{itemize}
    \item Designed and built new features for Teller, an enterprise
        point-of-sale system for municipal governments.
    \item Implemented plugins to integrate Teller with external vendors
        including Bank of America and Tyler Tech.
    \item Spearheaded company-wide transition to Git.
    \item Helped transition Teller from a Windows Desktop application to a
        web-based application.
\end{itemize}

\vspace{2pt}
\textbf{Taekwondo Instructor} - Ken Caryl ATA Martial Arts - Littleton, CO
\hfill Nov. 2015 - Aug. 2016

\vspace{2pt}
\textbf{Software Developer Intern} - Can/Am Technologies, Inc. - Lakewood, CO
\hfill Feb. 2013 - June 2013

\section*{Projects}
\textbf{Visplay} -
\href{https://gitlab.com/ColoradoSchoolOfMines/visplay}{gitlab.com/ColoradoSchoolOfMines/visplay}
- GPLv3 \hfill February 2018 - Present
\begin{itemize}
    \item Mines ACM project to create a digital signage system with a dynamic,
        hierarchical configuration system.
    \item I am working on design of the overall system's architecture and
        contributing in a project management role.
\end{itemize}

\textbf{Wii-Track} -
\href{https://github.com/ColoradoSchoolOfMines/wii-track}{github.com/ColoradoSchoolOfMines/wii-track}
- GPLv3 \hfill February 2018
\begin{itemize}
    \item Distributed inventory tracking using IOT technologies. Backed by AWS
        Lambda and DynamoDB.
    \item I worked on designing the overall system's architecture, set up the
        DynamoDB database, and implemented a AWS Lambda function to identify
        packages by weight.
    \item Our team presented the project in front of a panel of Dish Network
        executives.
    \item \textit{Awards:} Judges Favorite, Best Use of AWS, and Dish Network
        Challenge winner at HackCU IV.
\end{itemize}

\section*{Projects (Continued)}
\textbf{Virtual Reality Final Project} -
\href{https://github.com/CSM-Dream-Team/final-project}{github.com/CSM-Dream-Team/final-project}
- GPLv3 \hfill Aug. 2018 - Dec. 2018
\begin{itemize}
    \item Final project from an independent study in virtual reality under the
        supervision of Dr. Paone.
    \item We developed a new program architecture for virtual reality called
        \textit{Deferred Immediate Mode}.
\end{itemize}

\textbf{Wireless Debugging} -
\href{https://github.com/sumnerevans/wireless-debugging}{github.com/sumnerevans/wireless-debugging}
- Apache 2.0 \hfill May 2017 - June 2017
\begin{itemize}
    \item Mobile library and log-parsing web server to allow streaming of mobile
        app logs to a web UI console.
    \item I was the primary writer of the API specifications for communicating
        between each component.
    \item I built the log parsing library and the mobile API implementation for
        iOS.
    \item Built with four other students during the Mines CS Field Session under
        the supervision of Google.
\end{itemize}

\section*{Skills}
{\renewcommand\labelitemi{}
    \renewcommand\leftmargini{0pt}
    \begin{itemize}
        \item \textbf{Language Experience:} Python, C\#, JavaScript, C++, Java,
            {\fontfamily{ptm}\selectfont\LaTeX}, HTML, CSS, SQL
        \item \textbf{Tools:} Linux, Vim, Git, AWS, macOS, Windows, Visual
            Studio, Sublime Text, IntelliJ IDEA
    \end{itemize}
}

\section*{Awards and Honors}
\begin{itemize}
    \item Outstanding Graduating Senior (May 2018)
    \item Nominated for \textit{Student Employee of the Year} by Christopher
        Painter-Wakefield (May 2018)
    \item First Place at Google Games in Boulder (April 2018)
    \item Google C-MAPP scholarship recipient (January 2018)
    \item Member of the Tau Beta Pi Honor Society (November 2017 - Present)
    \item Won \textit{Grand Prize} at the Xilinx Pynq Hackathon with parking lot
        tracking project (October 2017)
    \item Deans List Fall 2016, Spring 2017, and Fall 2017
    \item Placed 3rd in 2016 Regional ACM International Collegiate Programming
        Contest (ICPC)
    \item Grand Master Emeritus Soon Ho Lee Scholarship from the H.U. Lee
        Memorial Foundation (June 2016)
\end{itemize}

\section*{Personal Achievements}
\begin{itemize}
    \item \textbf{Taekwondo}: 3rd Degree Black Belt, three time Colorado State
        Champion, Certified Trainer
    \item \textbf{Soccer}: Captain of high school team for three years, 2015
        Conference All Star and All Tournament Player
\end{itemize}

% \section*{Papers}
% \textbf{Dreams of Flight} -
% \href{http://www.rrcc.edu/sites/default/files/claro-sumnerevansFINAL.pdf}{Claro}
% \hfill May 2014
% \begin{itemize}
%     \item Creative writing piece about Orville and Wilbur Wright and the first
%         flight at Kitty Hawk.
% \end{itemize}

% \section*{Presentations}
% \textbf{Idris} -
% \href{https://github.com/sumnerevans/lug-idris}{github.com/sumnerevans/lug-idris}
% \hfill March 2018

\end{document}
