\documentclass[10.5pt,letterpaper]{article}
\usepackage[margin=0.65in]{geometry}
\usepackage{graphicx}
\usepackage[pdftex,pdfnewwindow=true]{hyperref}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage{sectsty}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\pagestyle{fancy}

\cfoot{Updated: \today}
\definecolor{header-blue}{HTML}{3D85C6}

\setlength{\parindent}{0pt}
\setlength{\parskip}{-2pt}
\sectionfont{\color{header-blue}\fontsize{11}{0}\selectfont\MakeUppercase}
\titlespacing*{\section}{0pt}{17pt}{8pt}
\pagenumbering{gobble} % No page number

\setlist[itemize]{noitemsep}
\setlength{\leftmargini}{20pt}

\begin{document}

\begin{center}
    \huge\textbf{Jonathan Sumner Evans} \\
    \vspace{3pt}
    \small \faPhone\ +1 (720) 459-1501
    \textbar\textbar\ \href{mailto:jonathanevans@mines.edu}{\faEnvelopeO\ jonathanevans@mines.edu}
    \textbar\textbar\ \href{http://sumnerevans.com}{\faGlobe\ sumnerevans.com}
    \textbar\textbar\ \faHome\ 25 Amaranth Dr., Littleton, CO 80127 \\
    \href{http://stackoverflow.com/users/2319844/sumner-evans}{\faStackOverflow\
    stackoverflow.com/users/2319844/sumner-evans}
    \textbar\textbar\ \href{https://www.linkedin.com/in/sumnerevans}{\faLinkedin\
    linkedin.com/in/sumnerevans}
    \textbar\textbar\ \href{https://github.com/sumnerevans}{\faGithub\
    github.com/sumnerevans}
    \rule{\textwidth}{0.5pt}
\end{center}

\section*{Education}
\textbf{Colorado School of Mines} - Golden, CO - B.S. Computer Science - 4.0 GPA
\hfill July 2016 - May 2018
\begin{itemize}
    \item Vice President of the Mines ACM Student Chapter and Secretary of the
        Mines Linux Users Group (LUG)
    \item Placed 3rd in 2016 Regional ACM ICPC
    \item \textbf{Notable Classes:} Operating Systems*, Algorithms, Computer
        Graphics*, Computer Simulation*, Virtual Reality*, Software Engineering,
        Advanced Software Engineering, Computer Organization, Linear Algebra,
        Data Structures \hfill\textit{* = currently enrolled}
\end{itemize}

\vspace{4pt}
\textbf{Red Rocks Community College} - Lakewood, CO - 67 Credit Hours - 4.0 GPA
\hfill Aug. 2012 - May 2016
\begin{itemize}
    \item Creative historical writing selected for publication in
        \textit{Claro}, an interdisciplinary scholarly journal.
    \item Presented at \textit{Claro} academic conference.
\end{itemize}

\section*{Skills}
{\renewcommand\labelitemi{}
    \renewcommand\leftmargini{0pt}
    \begin{itemize}
        \item \textbf{Language Experience:} Python, C\#, JavaScript (Ext JS,
            Node.js), C++, Java, \LaTeX, HTML, CSS, SQL
        \item \textbf{Design:} Website Design, Mockups, Requirements Gathering,
            Technical Specification
        \item \textbf{Tools and Operating Systems:} Linux, macOS, Windows, Vim,
            Visual Studio, Git, Sublime Text, IntelliJ IDEA
    \end{itemize}
}

\section*{Work Experience}
\textbf{Teachers Assistant (Data Structures)} - Colorado School of Mines -
Golden, CO \hfill Aug. 2017 - Present
\begin{itemize}
    \item Assist students during TA office hours and during the in-class lab
        sessions.
\end{itemize}


\vspace{4pt}
\textbf{Software Development Intern} - Kenzan - Denver, CO
\hfill June 2017 - Aug. 2017
\begin{itemize}
    \item Contributed to OSS projects on behalf of Kenzan including React and
        Node.
    \item Worked to improve Kenzan website by implementing CI/CD pipeline with
        a WebPack build.
\end{itemize}

\vspace{4pt}
\textbf{Software Developer} - Can/Am Technologies, Inc. - Lakewood, CO
\hfill July 2013 - Aug. 2016
\begin{itemize}
    \item Designed and built new features and plugins for Teller, an enterprise
        point-of-sale system for municipal governments.
    \item Spearheaded company-wide transition to Git.
    \item Helped transition Teller from a Windows Desktop application to a
        web-based application.
\end{itemize}

\vspace{4pt}
\textbf{Taekwondo Instructor} - Ken Caryl ATA Martial Arts - Littleton, CO
\hfill Nov. 2015 - Aug. 2016
\begin{itemize}
    \item Instructed colored belt (pre black belt) classes and junior leadership
        classes.
\end{itemize}

\vspace{4pt}
\textbf{Software Developer Intern} - Can/Am Technologies, Inc - Lakewood, CO
\hfill Feb. 2013 - June 2013
\begin{itemize}
    \item Designed and built an invoicing and time tracking system for internal
        use at Can/Am.
\end{itemize}

\section*{Portfolio}
\textbf{Wireless Debugging} -
\href{https://github.com/sumnerevans/wireless-debugging}{github.com/sumnerevans/wireless-debugging}
- Apache 2.0 License \hfill May 2017 - June 2017
\begin{itemize}
    \item Mobile SDK and log-parsing web server to allow streaming of mobile app
        logs to a web UI console.
    \item Built with team of 5 for CSCI 370 Computer Science Field Session under
        the supervision of Google.
\end{itemize}

\section*{Personal Achievements}
\begin{itemize}
    \item \textbf{Taekwondo}: 3rd Degree Black Belt, three time Colorado State
        Champion, Certified Trainer
    \item \textbf{Soccer}: Captain of high school team for three years, 2015
        Conference All Star, two years All Conference Player and All Tournament
        Player
\end{itemize}

\section*{Awards and Honours}
\begin{itemize}
    \item Deans List Fall 2016 and Spring 2017
    \item Grand Master Emeritus Soon Ho Lee Scholarship from the H.U. Lee
        Memorial Foundation (June 2016)
    \item Red Rocks Community College Phi Theta Kappa Honor Society (March 2013
        - May 2016)
\end{itemize}

\end{document}
